Standardization of ceramic shape: A case studay from the Iron Age pottery from northeastern Taiwan

### 2020-08-10 analysis/paper/paper.Rmd
add MANOVA test

@@

Petrographic analysis for 34 thin sections presents a high percentage of inclusions (15-50%), including argillite (15-40%), metasandstone (1-10%), sandstone fragments (1-6%), quartz (1-5%), and trace amounts of feldspar and slate. Particle sizes of range from 500 to 1300 microns. In general, the globular vessel fabric presents a mixture of fine, rounded argillite with a small amounts of rounded metasandstone and rounded to sub-angular monocrystalline quartz. This composition is consistent with the mineralogical composition of local raw materials found in the Yilan Plain [@Chen2016]. There are no substantial changes in the inclusions over time, indicating continuity in pottery fabric composition across the three periods. <!--Was this tested using statistics? If so, then state that there are no significant changes in the inclusions over time, and include that script in your supplementary materials.-->

>>>>

```{r}
library(readxl)
thin_section <- read_excel(here::here("analysis", "data", "raw_data", "kwl_petrography.xlsx"), 2)
sherd <- read_excel(here::here("analysis", "data", "raw_data", "kwl_petrography.xlsx"), 1)

# sum the columns of similar minerals
thin_section_combine <-
  thin_section %>%
  mutate(Quartz = `Monocrystalline quartz` + `Polycrystalline quartz`,
         Argillite_all = `Argillite` + `Reddish-brown Argillite`)

# prepare data for pca
thin_section_combine_pca <-
  thin_section_combine %>%
  select(4:5, 8:12, 17:18)

# PCA
pca1 <- prcomp(thin_section_combine_pca, scale. = TRUE)
# add phase
pca1$phase <- as.factor(thin_section_combine$phase)

# MANOVA
man_pca <- manova(pca1$x ~pca1$phase)
sum_man_all <- summary(man_pca, test="Pillai")

# get p value
sum_man_all_df <-
  as.data.frame(sum_man_all[4]) %>%
  mutate_if(is.numeric, round, 4) %>%
  select(-`stats.Df`, -`stats.num.Df`) %>%
  rename(`Pillai's trace` = `stats.Pillai`,
         `Approximate F value` = `stats.approx.F`,
         `degrees of freedom` = `stats.den.Df`,
         `Pr(>F)` = `stats.Pr..F.`)

pval_all <- signif(unname(sum_man_all_df[,'Pr(>F)'][1]), 4)
```

@@

Petrographic analysis for 34 thin sections presents a high percentage of inclusions (15-50%), including argillite (15-40%), metasandstone (1-10%), sandstone fragments (1-6%), quartz (1-5%), and trace amounts of feldspar and slate. Particle sizes of range from 500 to 1300 microns. In general, the globular vessel fabric presents a mixture of fine, rounded argillite with a small amounts of rounded metasandstone and rounded to sub-angular monocrystalline quartz. This composition is consistent with the mineralogical composition of local raw materials found in the Yilan Plain [@Chen2016]. There are no significant changes in the inclusions over time, indicating continuity in pottery fabric composition across the three periods (p = $`r pval_all`$) [@WangandMarwick2020].
